# Run overview

::: {.callout-note .benchmark_callouts title="Summary"}
This section provides a high-level overview of the pipeline run metrics.
:::

## Run summary

Summary of pipeline execution and infrastructure settings.

```{r}
#| label: run-overview-table
#| echo: false
#| include: false
#| results: hide
#| 
# Function to apply alpha to a hex color
apply_alpha <- function(color, alpha) {
  rgb <- col2rgb(color) / 255
  sprintf("rgba(%d, %d, %d, %.2f)", rgb[1] * 255, rgb[2] * 255, rgb[3] * 255, alpha)
}

calculate_min_width <- function(column_data) {
  max(nchar(as.character(column_data))) * 8  # Approximate width in pixels (adjust the multiplier as needed)
}

table_row_alpha_value <- 0.15


view_table <- merged_logs %>%
  mutate(
    userName = if("userName" %in% colnames(.)) userName else NA,
    workflow_revision = if("workflow_revision" %in% colnames(.)) workflow_revision else NA,
    "nextflow.version" = if("nextflow.version" %in% colnames(.)) `nextflow.version` else NA,
    "stats.succeedCount" = if("stats.succeedCount" %in% colnames(.)) `stats.succeedCount` else NA,
    "stats.failedCount" = if("stats.failedCount" %in% colnames(.)) `stats.failedCount` else NA,
    executors = if("executors" %in% colnames(.)) executors else NA,
    "computeEnv.config.region" = if("computeEnv.config.region" %in% colnames(.)) `computeEnv.config.region` else NA,
    "computeEnv.config.forge.type" = if("computeEnv.config.forge.type" %in% colnames(.)) `computeEnv.config.forge.type` else NA,
    "computeEnv.config.forge.maxCpus" = if("computeEnv.config.forge.maxCpus" %in% colnames(.)) `computeEnv.config.forge.maxCpus` else NA,
    "computeEnv.config.waveEnabled" = if("computeEnv.config.waveEnabled" %in% colnames(.)) `computeEnv.config.waveEnabled` else NA,
    "computeEnv.config.fusion2Enabled" = if("computeEnv.config.fusion2Enabled" %in% colnames(.)) `computeEnv.config.fusion2Enabled` else NA,
    "computeEnv.config.nvnmeStorageEnabled" = if("computeEnv.config.nvnmeStorageEnabled" %in% colnames(.)) `computeEnv.config.nvnmeStorageEnabled` else NA,
    "computeEnv.config.forge.gpuEnabled" = if("computeEnv.config.forge.gpuEnabled" %in% colnames(.)) `computeEnv.config.forge.gpuEnabled` else NA,
    "computeEnv.config.forge.ebsAutoScale" = if("computeEnv.config.forge.ebsAutoScale" %in% colnames(.)) `computeEnv.config.forge.ebsAutoScale` else NA
  ) %>%
  select(pipeline, group, run_id, userName, workflow_revision, "nextflow.version", version, 
         "stats.succeedCount", "stats.failedCount", executors, "computeEnv.config.region",
         "computeEnv.config.forge.type", "computeEnv.config.forge.maxCpus", "computeEnv.config.waveEnabled",
         "computeEnv.config.fusion2Enabled", "computeEnv.config.nvnmeStorageEnabled",
         "computeEnv.config.forge.gpuEnabled", "computeEnv.config.forge.ebsAutoScale") %>%
  rename(
    username = userName,
    Version = workflow_revision,
    Nextflow_version = "nextflow.version",
    platform_version = version,
    succeedCount = "stats.succeedCount",
    failedCount = "stats.failedCount", 
    executor = executors,
    region = "computeEnv.config.region",
    provisioning = "computeEnv.config.forge.type",
    max_cpu = "computeEnv.config.forge.maxCpus",
    waveEnabled = "computeEnv.config.waveEnabled",
    fusion_enabled = "computeEnv.config.fusion2Enabled",
    nvnmeStorageEnabled = "computeEnv.config.nvnmeStorageEnabled",
    gpu_enabled = "computeEnv.config.forge.gpuEnabled",
    ebs_autoscale = "computeEnv.config.forge.ebsAutoScale"
  ) %>%
  # Replace NA values in columns with enabled in name with false
  mutate(across(ends_with("enabled"), ~ifelse(is.na(.), FALSE, .)))

run_overview <- reactable(
  view_table,
  language = reactableLang(
    searchPlaceholder = "Filter"
    ),
  defaultColDef = colDef(
    align = "center",
    minWidth = 150
    ),
   columns = list(
    pipeline = colDef(name = "Pipeline<br>name",html = TRUE, align = "left",
                       style = list(whiteSpace = "nowrap", overflow = "hidden", textOverflow = "ellipsis"),
                      minWidth = 200,
                       ),
    group = colDef(name = "Group", html = TRUE, align = "left", minWidth = 150,),
    run_id = colDef(name = "Run ID", html = TRUE, minWidth = 200, align = "left"),
    username = colDef(name = "User<br>name", html = TRUE, minWidth = 180, align = "left"),
    Version = colDef(name = "Pipeline<br>version", html = TRUE),
    Nextflow_version = colDef(name = "Nextflow<br>version", html = TRUE),
    platform_version = colDef(name = "Platform<br>version", html = TRUE, minWidth = 180),
    succeedCount = colDef(name = "Tasks<br>succeeded", html = TRUE),
    failedCount = colDef(name = "Tasks<br>failed", html = TRUE),
    executor = colDef(name = "Executor"),
    region = colDef(name = "Region"),
    provisioning = colDef(name = "Provisioning<br>model", html = TRUE, minWidth = 150,),
    max_cpu = colDef(name = "Max<br>CPUs", html = TRUE),
    waveEnabled = colDef(name = "Wave<br>enabled", html = TRUE),
    fusion_enabled = colDef(name = "Fusion<br>enabled", html = TRUE),
    nvnmeStorageEnabled = colDef(name = "NVMe<br>enabled", html = TRUE),
    gpu_enabled = colDef(name = "GPU<br>enabled", html = TRUE),
    ebs_autoscale = colDef(name = "EBS<br>autoscale", html = TRUE)
     ),
  rowStyle = function(index) {
    group <- view_table$group[index]
    color <- groups_color_palette[[group]]
    color_with_alpha <- apply_alpha(color, table_row_alpha_value)
    list(background = color_with_alpha)
  },
  wrap = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  striped = FALSE,
  highlight = TRUE,
  searchable = TRUE,
  defaultPageSize = 20
)
```

::: {.callout-caution .benchmark_callouts collapse="false" icon="false"}
## {{< fa table >}} Click to display table

`r run_overview`
:::

## Run metrics

This section provides a visual overview of the pipeline run metrics. Task-derived efficiencies are recomputed from the task logs, and optional scheduler/VM metrics are added when machine CSVs are available.

```{r run-metrics}
library(RColorBrewer)
color_palette <- brewer.pal(8, "Set1")

css_style <- "
.reactable-cell .data-bar-text {
  margin-right: 30px;  # Adjust this value to increase/decrease the distance
}
"

cost_colname <- ""
cost_colname_used <- ""
cost_colname_unused <- ""

# Custom formatter for percentage column
format_percentage <- function(value) {
  sprintf("%.2f%%", value)
}

## Add cost information, if requested
if (grepl("cost",profile)) {
  all_runs <- unique(cost_table$run_id)
  
  run_cost <- cost_table %>% 
    group_by(run_id) %>%
    subset(!is.na(cost)) %>%
    summarise(cost = round(sum(cost),2),
              used_cost = round(sum(used_cost),2),
              unused_cost = round(sum(unused_cost),2)) %>%
    select(run_id,cost,used_cost,unused_cost)
  runs_with_some_cost <- run_cost$run_id
  # Check if there is an NA in run_cost$cost and if so, break
  if (!all(all_runs %in% runs_with_some_cost)){
    # Check if all IDs in all_runs are found in runs_with_some_cost and if not, break
    stop("Cost information is missing for some runs. Please check the cost report.")
  }
  
  ## run_cost will contain accurate cost, if AWS reports provided
  merged_logs <- merged_logs %>% select(-cost)
  merged_logs <- left_join(merged_logs,run_cost,by="run_id")
  cost_colname <- "Estimated<br>cost ($)"
}

if (params$aws_cost != "NA") {
  cost_colname        <- "Compute<br>cost ($)"
  cost_colname_used   <- "Used<br>compute<br>cost ($)"
  cost_colname_unused <- "Unused<br>compute<br>cost ($)"
}

## Select which columns to keep
if(grepl("cost",profile) & params$aws_cost != "NA") {
    merged_logs <- merged_logs %>% select(any_of(c("pipeline","group","run_id","Wall_time","duration","cpuTime","task_runtime_ms","cost","readBytes","writeBytes","cpuEfficiency","memoryEfficiency","pipeline_workdirSize_GB","pipeline_workdirSize_price","used_cost","unused_cost","nMachines","vmCpuH","vmMemGibH","schedAllocCpuEfficiency","schedAllocMemEfficiency","realVmCpuEfficiency","realVmMemEfficiency","realCpuH","realMemGibH","requestedCpuH","requestedMemGibH")))
}else {
  merged_logs <- merged_logs %>% select(any_of(c("pipeline","group","run_id","Wall_time","duration","cpuTime","task_runtime_ms","cost","readBytes","writeBytes","cpuEfficiency","memoryEfficiency","pipeline_workdirSize_GB","pipeline_workdirSize_price","nMachines","vmCpuH","vmMemGibH","schedAllocCpuEfficiency","schedAllocMemEfficiency","realVmCpuEfficiency","realVmMemEfficiency","realCpuH","realMemGibH","requestedCpuH","requestedMemGibH")))
}

metrics_reactable <- merged_logs %>%
  mutate(readBytes = round(readBytes,0),
         writeBytes = round(writeBytes,0),
         cpuEfficiency = round(cpuEfficiency,0),
         memoryEfficiency = round(memoryEfficiency,4),
         task_runtime_time = sapply(task_runtime_ms, milliseconds_to_hms)) %>%
  arrange(pipeline)

if("pipeline_workdirSize_GB" %in% colnames(metrics_reactable)) {
  metrics_reactable <- metrics_reactable %>%
    mutate(pipeline_workdirSize_GB = round(pipeline_workdirSize_GB,2),
           pipeline_workdirSize_price = round(pipeline_workdirSize_price,2),)
}

# If cost profile not selected, drop costs
if (!grepl("cost",profile) ) {
  metrics_reactable <- metrics_reactable %>% select(-cost)
}

run_metrics_table <- reactable(metrics_reactable,
                              language = reactableLang(
                                searchPlaceholder = "Filter"
                              ),
                              defaultColDef = colDef(
                                align = "center",
                                minWidth = 180),
                              columns = list(
                                pipeline = colDef(name = "Pipeline<br>name", html = TRUE,align = "left",
                                                  width = 200,  # Set an appropriate width
                                                  style = list(whiteSpace = "nowrap", overflow = "hidden", 
                                                               textOverflow = "ellipsis")
                                ),
                                group = colDef(name = "group",align = "left",),
                                run_id = colDef(name = "Run ID", html = TRUE, minWidth = 180, align = "left",),
                                Wall_time = colDef(name = "Wall<br>time", html = TRUE,
                                                   cell = data_bars(metrics_reactable, fill_color = color_palette[1],
                                                                    fill_by = "duration",
                                                                    force_outside = c(0,0.5*max(metrics_reactable$duration))
                                                                    )
                                ),
                                duration = colDef(show = FALSE),
                                cpuTime    = colDef(name = "CPU<br>time (hours)", html = TRUE, format = colFormat(digits = 1),
                                                 cell = data_bars(metrics_reactable, text_color = "black",  fill_color = color_palette[2],
                                                                  fill_by = "cpuTime", 
                                                                  text_position = "inside-end", force_outside = c(0,0.5*max(metrics_reactable$cpuTime))
                                                                  )
                                                 ),
                                task_runtime_ms = colDef(show = FALSE),
                                task_runtime_time = colDef(name = "Total task<br>runtime", html = TRUE,
                                                   cell = data_bars(metrics_reactable, fill_color = color_palette[8],
                                                                    fill_by = "task_runtime_ms",
                                                                    force_outside = c(0,0.5*max(metrics_reactable$task_runtime_ms)))
                                ),
                              cost       = colDef(name = cost_colname, html = TRUE, 
                                              cell = data_bars(metrics_reactable, fill_color = color_palette[3], fill_by = "cost",
                                                               force_outside = c(0,0.5*max(metrics_reactable$cost))
                                                               )),
                              used_cost   = colDef(name = cost_colname_used, html = TRUE, 
                                                    cell = data_bars(metrics_reactable, fill_color = color_palette[3], 
                                                                     fill_by = "used_cost",
                                                                     force_outside = c(0,0.5*max(metrics_reactable$used_cost))
                                                                     )),
                              unused_cost       = colDef(name = cost_colname_unused, html = TRUE, 
                                                    cell = data_bars(metrics_reactable, fill_color = color_palette[3], fill_by = "unused_cost",
                                                                     force_outside = c(0,0.5*max(metrics_reactable$unused_cost))
                                                                     )),
                               pipeline_workdirSize_GB       = colDef(name = "Workdir size (GB)", html = TRUE, 
                                              cell = data_bars(metrics_reactable, fill_color = color_palette[3], fill_by = "pipeline_workdirSize_GB",
                                                               force_outside = c(0,0.5*max(metrics_reactable$cost))
                                                               )),
                               pipeline_workdirSize_price       = colDef(name = "Workdir storage<br>cost monthly ($)", html = TRUE, 
                                              cell = data_bars(metrics_reactable, fill_color = color_palette[3], fill_by = "pipeline_workdirSize_price",
                                                               force_outside = c(0,0.5*max(metrics_reactable$cost))
                                                               )),
                                readBytes  = colDef(name = "Read<br>(GB)", html = TRUE, 
                                                   cell = data_bars(metrics_reactable, fill_color = color_palette[4], fill_by = "readBytes",
                                                                    force_outside = c(0,0.5*max(metrics_reactable$readBytes))
                                                                    )),
                                writeBytes = colDef(name = "Write<br>(GB)", html = TRUE, 
                                                    cell = data_bars(metrics_reactable, fill_color = color_palette[5], fill_by = "writeBytes",
                                                                     force_outside = c(0,0.5*max(metrics_reactable$writeBytes))
                                                                     )),
                                cpuEfficiency = colDef(name = "Task CPU<br>efficiency (%)", html = TRUE, 
                                                       cell = data_bars(metrics_reactable, fill_color = color_palette[6], fill_by = "cpuEfficiency",
                                                                        force_outside = c(0,0.5*max(metrics_reactable$cpuEfficiency))
                                                                        )),
                                memoryEfficiency = colDef(name = "Task memory<br>efficiency (%)", html = TRUE,
                                                          cell = data_bars(metrics_reactable, fill_color = color_palette[7], fill_by = "memoryEfficiency",
                                                                           force_outside = c(0,0.5*max(metrics_reactable$memoryEfficiency))
                                                                           ))
                              ),
                              rowStyle = function(index) {
                                group <- view_table$group[index]
                                color <- groups_color_palette[[group]]
                                color_with_alpha <- apply_alpha(color, table_row_alpha_value)
                                list(background = color_with_alpha)
                              },
                              style = list(css = css_style),
                              wrap = FALSE,
                              resizable = TRUE,
                              bordered = TRUE,
                              striped = FALSE,
                              highlight = TRUE,
                              filterable = FALSE,
                              searchable = TRUE,
                              defaultPageSize = 20,
                              elementId = "metrics-table"
)
```

```{r download-button-run-overview}
library(htmltools)

download_button <- HTML('
  <style>
    .download-button {
      background-color: #160F26; /* Green background */
      border: none; /* Remove borders */
      color: white; /* White text */
      padding: 10px 10px; /* Some padding */
      text-align: center; /* Center the text */
      text-decoration: none; /* Remove underline */
      display: inline-block; /* Make the button inline */
      font-size: 17px; /* Increase font size */
      margin: 4px 2px; /* Add some margin */
      cursor: pointer; /* Pointer/hand icon */
      border-radius: 5px; /* Rounded corners */
    }
    .download-button:hover {
      background-color: #0DC09D; /* Darker green on hover */
    }
  </style>
  <button class="download-button" onclick="Reactable.downloadDataCSV(\'metrics-table\', \'run_overview.csv\')">
    Download as CSV
  </button>
')
```

::: {.callout-caution .benchmark_callouts collapse="true" icon="false"}
## {{< fa table >}} Click to display table

`r run_metrics_table`

<center>`r download_button`</center>
:::

```{r}
# Set dynamic figure height
fig_height <- 10 + 3 * n_groups
```


```{r run-metrics-plot}
#| fig-width: 12
#| fig-height: !expr fig_height

## Generate table for metrics plot based on whether cost parameter is set to true
if (grepl("cost",profile)) {
    metrics_table <- merged_logs %>% select(any_of(c("pipeline","group","run_id","Wall_time","duration","cpuTime","readBytes","writeBytes","cpuEfficiency","memoryEfficiency","task_runtime_ms","pipeline_workdirSize_GB","pipeline_workdirSize_price","cost","used_cost","unused_cost")))
    if("pipeline_workdirSize_GB" %in% colnames(metrics_table)){
      metrics <- c("Wall_time","cost","used_cost","unused_cost","task_runtime_ms","cpuTime","readBytes", "writeBytes", "cpuEfficiency", "memoryEfficiency","pipeline_workdirSize_GB","pipeline_workdirSize_price")
      ## Create a labeler for facets
      metrics_formatted <- c("Wall time (HH:MM:SS)","Estimated compute cost ($)","Estimated used compute cost ($)","Estimated unused compute cost ($)", "Total task runtime (HH:MM:SS)","CPU time (hours)", "Read (GB)", "Write (GB)", "Task CPU efficiency (%)", "Task memory efficiency (%)","Workdir size (GB)","Workdir storage cost monthly ($)")
    }else{
      metrics <- c("Wall_time","cost","used_cost","unused_cost","task_runtime_ms","cpuTime","readBytes", "writeBytes", "cpuEfficiency", "memoryEfficiency")
      metrics_formatted <- c("Wall time (HH:MM:SS)","Estimated compute cost ($)","Estimated used compute cost ($)","Estimated unused compute cost ($)", "Total task runtime (HH:MM:SS)","CPU time (hours)", "Read (GB)", "Write (GB)", "Task CPU efficiency (%)", "Task memory efficiency (%)")
    }

    if (params$aws_cost != "NA") {
      # Replace Estimated cost ($) with Accurate<br>cost ($) in vector metrics_formatted
      metrics_formatted[metrics_formatted == "Estimated compute cost ($)"]        <- "Accurate compute cost ($)"
      metrics_formatted[metrics_formatted == "Estimated used compute cost ($)"]   <- "Accurate used compute cost ($)"
      metrics_formatted[metrics_formatted == "Estimated unused compute cost ($)"] <- "Accurate unused compute cost ($)"
    }
    labels <- setNames(metrics_formatted, metrics)
  } else {
    metrics_table <- merged_logs %>% select(any_of(c("pipeline","group","run_id","Wall_time","duration","cpuTime","readBytes","writeBytes","cpuEfficiency","memoryEfficiency","task_runtime_ms","pipeline_workdirSize_GB","pipeline_workdirSize_price")))
    
    if("pipeline_workdirSize_GB" %in% colnames(metrics_table)){
      metrics <- c("Wall_time","cpuTime","task_runtime_ms","readBytes", "writeBytes", "cpuEfficiency", "memoryEfficiency","pipeline_workdirSize_GB","pipeline_workdirSize_price")
      ## Create a labeler for facets
      metrics_formatted <- c("Wall time (HH:MM:SS)", "CPU time (hours)","Total task runtime (HH:MM:SS)", "Read (GB)", "Write (GB)", "Task CPU efficiency (%)", "Task memory efficiency (%)","Workdir size (GB)","Workdir storage cost monthly ($)")
    }else{
    metrics_table <- merged_logs %>% select(any_of(c("pipeline","group","run_id","Wall_time","duration","cpuTime","readBytes","writeBytes","cpuEfficiency","memoryEfficiency","task_runtime_ms")))
    metrics <- c("Wall_time","cpuTime","task_runtime_ms","readBytes", "writeBytes", "cpuEfficiency", "memoryEfficiency")
    ## Create a labeler for facets
    metrics_formatted <- c("Wall time (HH:MM:SS)", "CPU time (hours)","Total task runtime (HH:MM:SS)", "Read (GB)", "Write (GB)", "Task CPU efficiency (%)", "Task memory efficiency (%)")
    }

    labels <- setNames(metrics_formatted, metrics)
  }

metrics_table <- metrics_table %>% arrange(pipeline)

metrics_table_long <- metrics_table %>%
  mutate("Wall_time" = as.numeric(duration),
         "readBytes" = as.numeric(readBytes),
         "writeBytes" = as.numeric(writeBytes)
         ) %>%
  pivot_longer(cols = metrics,
               names_to = "Metric", values_to = "Value") %>%
  # Round all values except wall time and cost to 0 decimal places
  mutate(Value = if_else(Metric %in% c("Wall_time","task_runtime_ms","cost","used_cost","unused_cost"),Value,round(Value, 0))
         )

## Set order of facets
metrics_table_long$Metric <- factor(metrics_table_long$Metric,
                                    levels = metrics)

## Reverse order for flipped barplot
metrics_table_long$group <- factor(metrics_table_long$group, levels = rev(levels(metrics_table_long$group)))

## If a pipeline was run more than once, we show the mean for the barplot and points for the replicates. The text also shows the mean and is repositioned.
if(n_runs_max > 1){
  # Calculate mean values for text and text positioning
  means <- metrics_table_long %>%
    ungroup() %>%
    group_by(Group,Metric,pipeline) %>%
    summarise(mean_points = mean(as.numeric(Value)),
              max_value = max(as.numeric(Value))) %>%
    mutate(Formatted_Value = ifelse(Metric %in% c("Wall_time","task_runtime_ms"), sapply(mean_points, milliseconds_to_hms), 
                                      if_else(Metric == "cost",as.character(round(mean_points,2)),
                                              as.character(round(mean_points, 0))))
           )
  

  metrics_plot <- ggplot(metrics_table_long,
                         aes(x = Value, y = pipeline, group = group)
                         ) +
    geom_bar(aes(fill = group),stat = "summary",fun.y = "mean", position = "dodge", width = 0.75, color = "#160F26") +
    scale_fill_manual(values = groups_color_palette) +
    geom_point(aes(fill = group,
                   text = paste("run_id: ", run_id,"\n",
                                "Value: ", ifelse(Metric %in% c("Wall_time","task_runtime_ms"), sapply(Value, milliseconds_to_hms), as.character(Value)))
                                ),
               position = position_dodge(width = 0.75),  size = 3,
               #color = "black", show.legend = FALSE
               shape = 21, color = "black", show.legend = FALSE
               )
  
}else{ # If a pipeline was run only once
  metrics_table_long <- metrics_table_long %>%
    mutate(Formatted_Value = ifelse(Metric %in% c("Wall_time","task_runtime_ms"), sapply(Value, milliseconds_to_hms), as.character(Value)))
  
  metrics_table_long$group <- factor(metrics_table_long$group, levels = levels(metrics_table_long$group))

  metrics_plot <- ggplot(metrics_table_long,
                         aes(x = Value, y = pipeline, fill = group)) +
      geom_bar(stat = "identity", position = "dodge", width = 0.75,color = "#160F26") +
      geom_text(aes(label = pad_labels(ifelse(Metric %in% c("Wall_time","task_runtime_ms"), Formatted_Value, Value))),
            position = position_dodge(width = 0.75),
            hjust = -0.2, 
            size = 3.5,
            color = "#160F26"
            ) +
    scale_fill_manual(values = groups_color_palette)
}

metrics_plot <- metrics_plot + 
  facet_wrap(~ Metric, scales = "free_x", ncol = 2, labeller = as_labeller(labels)) +
  labs(
    x = "",
    y = "",
    fill = "group"
  ) +
  theme(legend.position = "top") +
  # Reverse order of legend keys
  guides(fill = guide_legend(reverse = TRUE)) +
  # Hide x-axis completely
  theme(axis.title.x = element_blank(),
        # axis.text.x = element_blank(),
        # axis.ticks.x = element_blank(),
        axis.line.x = element_blank()) +
  seqera_light_theme() +
  scale_x_continuous(limits = expand_x_limits) 

if(n_runs_max > 1){
  ggplotly(metrics_plot, tooltip = c("text"))
}else{
  metrics_plot
}
```

```{r vm-metrics-table}
#| echo: false
#| results: asis

vm_metrics_cols <- c("nMachines", "vmCpuH", "vmMemGibH", "schedAllocCpuEfficiency", "schedAllocMemEfficiency", "realVmCpuEfficiency", "realVmMemEfficiency", "realCpuH", "realMemGibH", "requestedCpuH", "requestedMemGibH")

if (all(vm_metrics_cols %in% colnames(metrics_reactable)) && any(!is.na(metrics_reactable$vmCpuH))) {
  cat("## Scheduler VM metrics\n\n")
  cat("These values are computed from optional machine CSVs when they are provided alongside each run dump. Task efficiencies are derived from task logs, while VM efficiencies relate those task metrics back to total machine lifetime capacity.\n\n")

  vm_metrics_table <- metrics_reactable %>%
    select(pipeline, group, run_id, all_of(vm_metrics_cols)) %>%
    mutate(
      vmCpuH = round(vmCpuH, 2),
      vmMemGibH = round(vmMemGibH, 2),
      schedAllocCpuEfficiency = round(schedAllocCpuEfficiency, 2),
      schedAllocMemEfficiency = round(schedAllocMemEfficiency, 2),
      realVmCpuEfficiency = round(realVmCpuEfficiency, 2),
      realVmMemEfficiency = round(realVmMemEfficiency, 2),
      realCpuH = round(realCpuH, 2),
      realMemGibH = round(realMemGibH, 2),
      requestedCpuH = round(requestedCpuH, 2),
      requestedMemGibH = round(requestedMemGibH, 2)
    )

  vm_metrics_reactable <- reactable(
    vm_metrics_table,
    language = reactableLang(searchPlaceholder = "Filter"),
    defaultColDef = colDef(align = "center", minWidth = 140),
    columns = list(
      pipeline = colDef(name = "Pipeline<br>name", html = TRUE, align = "left"),
      group = colDef(align = "left"),
      run_id = colDef(name = "Run ID", align = "left"),
      nMachines = colDef(name = "Machines"),
      vmCpuH = colDef(name = "VM CPU<br>hours", html = TRUE),
      vmMemGibH = colDef(name = "VM memory<br>GiB hours", html = TRUE),
      schedAllocCpuEfficiency = colDef(name = "Scheduler CPU<br>efficiency (%)", html = TRUE),
      schedAllocMemEfficiency = colDef(name = "Scheduler memory<br>efficiency (%)", html = TRUE),
      realVmCpuEfficiency = colDef(name = "Real VM CPU<br>efficiency (%)", html = TRUE),
      realVmMemEfficiency = colDef(name = "Real VM memory<br>efficiency (%)", html = TRUE),
      realCpuH = colDef(name = "Real CPU<br>hours", html = TRUE),
      realMemGibH = colDef(name = "Real memory<br>GiB hours", html = TRUE),
      requestedCpuH = colDef(name = "Requested CPU<br>hours", html = TRUE),
      requestedMemGibH = colDef(name = "Requested memory<br>GiB hours", html = TRUE)
    ),
    wrap = FALSE,
    resizable = TRUE,
    bordered = TRUE,
    striped = FALSE,
    highlight = TRUE,
    searchable = TRUE,
    defaultPageSize = 20
  )

  print(vm_metrics_reactable)
}
```
