---
format: 
  html:
    include-in-header:
      - text: |
          <link href="https://cdn.datatables.net/1.10.24/css/jquery.dataTables.css" rel="stylesheet"/>
          <link href="https://cdn.datatables.net/buttons/1.7.0/css/buttons.dataTables.min.css" rel="stylesheet"/>
          <script src="https://cdn.datatables.net/buttons/1.7.0/js/dataTables.buttons.min.js"></script>
          <script src="https://cdn.datatables.net/buttons/1.7.0/js/buttons.html5.min.js"></script>
---

# Task overview

::: {.callout-note .benchmark_callouts title="Summary"}
This section provides an overview of task-level metrics for instance usage and runtime metrics.
:::

## Task instance usage

::: {.callout-tip .benchmark_callouts title="Plot interaction" collapse="true"}
-   Hover over any bar to see the number of tasks per instance type
-   Single-click on entries in the legend to hide specific instance types
-   Double-click on entries in the legend to show specific instance types
:::


```{r task-instance-usage-plot}
#| fig-width: 12
#| fig-height: 12

## Use the tasks logs to summarize how many different tasks were run on which instance types
summary_tasks <- task_data %>%
  group_by(run_id,group, machineType) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  arrange(desc(n))

## Replace NA by "HPC" for slurm runs
executors <- unique(task_data$executor)
if("local" %in% executors){
  summary_tasks$machineType[is.na(summary_tasks$machineType)] <- "local"
}else{
  summary_tasks$machineType[is.na(summary_tasks$machineType)] <- "HPC"
}


## Add pipeline name to run_id
summary_tasks <- full_join(summary_tasks,merged_logs %>% select(run_id,pipeline),by="run_id") %>%
  select(group,pipeline,run_id,machineType,n)

summary_tasks$pipeline <- factor(summary_tasks$pipeline,
                               levels = rev(pipeline_order))

# Split the data by the facet variable
split_data <- summary_tasks %>%
  split(.$pipeline)

summary_tasks$Group <- factor(summary_tasks$group,
                              levels = unique(seqera_platform_logs@group))

## If a pipeline was run more than once, we modify how we plot the barplots 
if(n_runs_max > 1){
  instance_type_plot <- ggplot(summary_tasks, aes(x = paste(group,run_id,sep=" : "), y = n,
                                                fill = machineType,
                                                text = paste("Tasks: ",n,"\n",
                                                             "Instance type: ",machineType,
                                                             sep="")))
  x_axis_mod <- theme(axis.text.x = element_text(angle = 45, hjust = 1))
}else{
  instance_type_plot <- ggplot(summary_tasks, aes(x = group, y = n,
                                                fill = machineType,
                                                text = paste("Tasks: ",n,"\n",
                                                             "Instance type: ",machineType,
                                                             sep="")))
  x_axis_mod <- theme(axis.text.x = element_text(angle = 90, hjust = 1))
}

names(instance_palette) <- unique(summary_tasks$machineType)
instance_type_plot <- instance_type_plot +
  geom_bar(stat = "identity", color = "black", position = "stack") +
  labs(
    x = "",
    y = "Number of tasks",
    fill = "group"
  ) +
  seqera_light_theme() +
  theme(strip.text = element_text(size = 12),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)),
        panel.spacing.y = unit(2, "line"),
        plot.margin = unit(c(1, 1, 1, 1), "cm"),
        legend.position = "right",
        legend.title=element_text(face = "bold")
        ) +
  facet_wrap(~ pipeline, scales = "free_y", ncol = 2) +
  scale_fill_manual(values = instance_palette) +
  scale_y_continuous(limits = expand_x_limits,breaks = scales::pretty_breaks(n = 5), labels = function(x) ifelse(x == floor(x), x, NA)) +
  x_axis_mod

ggplotly(instance_type_plot, tooltip="text") %>%
  set_ggplotly_font() %>%
  plotly::layout(
    hovermode='x',
    margin = list(r = 200),  # Increase the right margin
    legend = list(
      x = 1.02,  # Position the legend outside the plot area
      y = 1,
      orientation = "v",
      font = list(size = 14)  # Adjust the font size if needed
    )
  ) %>%
  htmlwidgets::onRender("
    function(el, x) {
      var legendItems = el.querySelectorAll('.legendtext');
      legendItems.forEach(function(item) {
        item.style.width = '100px';  // Adjust the width as needed
        item.style.whiteSpace = 'normal';  // Allow wrapping
      });
    }
  ")
```

## Task metrics

This section provides a comparison and overview between staging and run times for tasks for each pipeline across these groups: `r groups_string`.

The different times for tasks are defined as follows:

-   **Wait time**: The time taken from submission to the start of the task.
-   **Staging time**: The time taken to stage and unstage the task before and after execution.
-   **Real time**: The time taken to execute the task.
-   **Task duration**: The elapsed time from task start to task completion, which corresponds to staging time plus real time.

For more detailed explanation of metrics shown in the table below the task plots, please see the [Nextflow reports documentation](https://www.nextflow.io/docs/latest/tracing.html).

::: {.callout-tip .benchmark_callouts title="Plot interaction" collapse="true"}
-   Single-click on any point to highlight the specific process in the table below.
-   Double-click on any whitespace in the plot to unselect a point.
:::

```{r, results='asis'}
#| label: task-level-plots
#| fig-width: 12
#| fig-height: 12
#| warning: false

## alpha value for the background color of the table
row_alpha_value <- 0.15
point_alpha <- 1
point_size <- 2

for(pipe in unique(task_data$pipeline)){
  
  #### Task staging and run times
  pipe_parsed <- gsub("/","_",pipe)
  cat(paste0("### ",pipe,paste0("{#sec-task-",pipe_parsed,"}"), " \n"))
  
  group1 <- as.character(unique(task_data$group)[1])
  group2 <- as.character(unique(task_data$group)[2])
  
  #### Cost plots
  if(grepl("cost",profile)){
    
    # cat(paste('The plots in this section show the cost distribution of tasks per process between the two groups. Tasks are grouped by processes on the x axis, so to show which process has a large cost spread across tasks and how this differs between groups. \n\n',sep=""))
    
    pipe_task_data_cost<- task_data %>%
      subset(pipeline == pipe) %>%
      select(run_id,pipeline,group,process,name,name_short,hash,runtime_mins,waittime_mins,staging_time_mins,realtime_mins)
    pipe_task_data_cost$hash <- gsub("/","",pipe_task_data_cost$hash)
    
    cost_table_pipe <- cost_table %>%
      subset(pipeline == pipe)
    
    cost_data_pipe_task <- full_join(cost_table_pipe,pipe_task_data_cost,by=c("run_id","pipeline","group","process","hash")) 
    cost_data_pipe_task <- cost_data_pipe_task %>%
      mutate(process_short = paste(str_extract(process, "[^:]+$"),sep=" - "))
    
    ## Sort processes based on most variation in cost between groups
    process_sum_cost <- cost_data_pipe_task %>%
      group_by(process_short,group) %>%
      summarise(sum_cost = mean(cost)) %>%
      ungroup() %>%
      group_by(process_short) %>%
      summarise(cost_sd = sd(sum_cost)) %>%
      ungroup() %>%
      arrange(desc(cost_sd))
    
    cost_data_pipe_task$process_short <- factor(cost_data_pipe_task$process_short, levels = process_sum_cost$process_short)
  
    shared_cost_data_pipe <- SharedData$new(cost_data_pipe_task, key = ~name, group = pipe)
  
    cost_task_time <- ggplot(shared_cost_data_pipe,
                             aes(x = process_short,
                                 y = cost,
                                 text = paste("Task name: ",name,"\n",
                                              "Task cost:",cost,sep=""))) +
      ## Add a boxplot with color = group that is dodged by group
      geom_boxplot(aes(color = group)) +
      geom_point(aes(color = group),position = position_dodge(width = 0.9), alpha = 1) +
      scale_color_manual(values = groups_color_palette) +
      labs(x = "Processes",
           y = "Task cost ($)",
           title = "Per task cost") +
      seqera_light_theme() +
      theme(plot.margin = unit(c(t = 1, r =1, b = 1.3, l = 1), "cm")
            ) +
      theme(axis.text.x = element_blank(),
            plot.title = element_text(size = plot_title_size)) +
      guides(shape = 21)
    
      cost_task_time_plotly <- ggplotly(cost_task_time, tooltip = "text")
      
      hideOutliers <- function(x) {  
      if (x$hoverinfo == 'y') {  
        x$marker = list(opacity = 0)
        x$hoverinfo = NA    
        }  
      return(x)  
    }

    n_groups <- length(unique(cost_data_pipe_task$group))
    cost_task_time_plotly[["x"]][["data"]] <- map(cost_task_time_plotly[["x"]][["data"]], ~ hideOutliers(.))
    
    ## Fix ggplotly legend
    cost_task_time_plotly <- cost_task_time_plotly %>% style(cost_task_time_plotly,showlegend = FALSE, traces = 1:n_groups)
    cost_task_time_plotly <- cost_task_time_plotly %>% style(cost_task_time_plotly,showlegend = TRUE, traces = (n_groups+1):(n_groups*2))
    
    ## Make boxplot not interactive
    cost_task_time_plotly <- cost_task_time_plotly %>% style(cost_task_time_plotly, hoverinfo = "none", traces = 1:n_groups)
      
        
      print(htmltools::tagList(
         cost_task_time_plotly %>%
          layout(hoverlabel = list(align = "left"),
                 boxmode = "group") %>%
          highlight(on = "plotly_click", off = "plotly_doubleclick", opacityDim = 0.1) %>%
          set_ggplotly_font() %>% 
          toWebGL()
        )
      )
    
    cost_data_pipe_task_table <- cost_data_pipe_task %>%
      select(group,run_id,hash,name,cost,used_cost,unused_cost)
    
    ## Set order of Groups
    cost_data_pipe_task_table$group <- factor(cost_data_pipe_task_table$group,
                                              levels = unique(seqera_platform_logs@group))
    
    shared_data_cost_table <- SharedData$new(cost_data_pipe_task_table, key = ~name, group = pipe)
    
    rgba_colors <- sapply(groups_color_palette, hex_to_rgba, alpha = row_alpha_value)[1:length(unique(cost_data_pipe_task_table$group))]
    pipe_cost_table <- div(class = "scrollable-table",
                             datatable(shared_data_cost_table,
                                   class = 'nowrap',
                                   escape = FALSE,
                                   colnames = c("Group" = "group", ## Order of colnames is important here!!!
                                                "Run ID" = "run_id",
                                                "Task<br/>hash" = "hash",
                                                "Compute cost" = "cost",
                                                "Used compute cost" = "used_cost",
                                                "Unused compute cost" = "unused_cost",
                                                "Task name" = "name"),
                                   selection="none",
                                   rownames= FALSE,
                                   options = list(autoWidth = FALSE,
                                                  language = list(search = 'Filter:'),
                                                  pageLength = 5,
                                                  order = list(list(2, 'asc')),
                                                  initComplete = JS(
                                                    "function(settings, json) {",
                                                    "$('table').css({'font-size': '17px'});",
                                                    "}"
                                                  ))
                                   ) %>%
        formatStyle(
          'Group',
          target = 'row',
          backgroundColor = styleEqual(
            names(rgba_colors),
            rgba_colors
            )
        )
      )
  
      print(htmltools::tagList(
        tags$style(HTML("
      .dataTable thead th {
        background-color: #160f26 !important;
        color: white !important;
        text-align: left !important;
        white-space: nowrap;
      }
      .dataTable tbody td {
        text-align: left !important;
        white-space: nowrap;
      }
      .scrollable-table {
        width: 100%;
        overflow-x: auto;
      }
      /* Style for the download button */
      .dt-button {
        background-color: #160F26 !important;
        border: none !important;
        color: white !important;
        padding: 10px 10px !important;
        text-align: center !important;
        text-decoration: none !important;
        display: inline-block !important;
        font-size: 17px !important;
        margin: 4px 2px !important;
        cursor: pointer !important;
        border-radius: 5px !important;
      }
      .dt-button:hover {
        background-color: #0DC09D !important;
      }
    ")
        ),
      pipe_cost_table))
  }
  
  pipe_task_data_plot <- task_data %>%
    subset(pipeline == pipe)

  
  ####
  #### Code chunk that will be run if comparing 2 groups with 1 run each (Quicklaunches)
  ####
  if (benchmark_scenario == "2groups_1run") {
    group1 <- as.character(unique(pipe_task_data_plot$group)[1])
    group2 <- as.character(unique(pipe_task_data_plot$group)[2])
    pipe_tasks_data <- task_data %>%
      subset(pipeline == pipe)
    
    ## Calculate the staging difference between the two groups
    pipe_staging_time <- pipe_tasks_data %>%
      select(pipeline,group,process,process_short,name,name_short,staging_time_mins) %>%
      group_by(pipeline,process,process_short,name,name_short) %>%
      pivot_wider(names_from = group, values_from = staging_time_mins,values_fn = sum) %>%
      mutate("staging_diff_min" = !!sym(group1) - !!sym(group2)) %>%
      ungroup() %>%
      arrange(desc(staging_diff_min))
    
    ## Calculate the realtime difference between the two groups
    pipe_tasks_realtime <- pipe_tasks_data %>%
      select(pipeline,group,process,process_short,name,name_short,realtime_mins) %>%
      group_by(pipeline,process,process_short,name,name_short) %>%
      pivot_wider(names_from = group, values_from = realtime_mins,values_fn = sum) %>%
      mutate("realtime_diff_min" = !!sym(group1) - !!sym(group2)) %>%
      ungroup() %>%
      arrange(desc(realtime_diff_min))
    
    shared_data_staging <- SharedData$new(pipe_staging_time, key = ~name, group = pipe)
    shared_data_realtimes <- SharedData$new(pipe_tasks_realtime,   key = ~name, group = pipe)
    
    ## Realtime task plot
    pipe_task_staging_plot <- ggplot(shared_data_staging, 
           aes(x = get(group1), 
               y = get(group2),
               text = paste("Task name: ",name_short,"\n",
                             group1, " : ",sprintf("%02d:%02d:%02d", floor(get(group1) / 60), floor(get(group1) %% 60), round((get(group1) %% 1) * 60)),"\n",
                             group2, " : ",sprintf("%02d:%02d:%02d", floor(get(group2) / 60), floor(get(group2) %% 60), round((get(group2) %% 1) * 60)),"\n",
                                                        sep=""),
               group = staging_diff_min)) +
    geom_point(size = point_size, alpha = point_alpha, color = "#160F26") +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
    labs(
      x = group1,
      y = group2,
      color = "Pipeline",
      title = "Staging time (minutes)"
    ) +
    seqera_light_theme() +
    theme(legend.position = "none",
          plot.margin = unit(c(t = 1, r =1, b = 1.3, l = 1), "cm"),
          plot.title = element_text(size = plot_title_size),
    )
    
    ## Realtime task plot
    pipe_task_realtime_plot <- ggplot(shared_data_realtimes, 
           aes(x = get(group1), 
               y = get(group2),
               text = paste("Task name: ",name_short,"\n",
                             group1, " : ",sprintf("%02d:%02d:%02d", floor(get(group1) / 60), floor(get(group1) %% 60), round((get(group1) %% 1) * 60)),"\n",
                             group2, " : ",sprintf("%02d:%02d:%02d", floor(get(group2) / 60), floor(get(group2) %% 60), round((get(group2) %% 1) * 60)),"\n",
                                                        sep=""),
               group = realtime_diff_min)) +
    geom_point(size = 2, alpha = 1, color = "#160F26") +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
    labs(
      x = group1,
      y = group2,
      color = "Pipeline",
      title = "Real time (minutes)"
    ) + 
    seqera_light_theme() +
    theme(legend.position = "none",
          plot.margin = unit(c(t = 1, r =1, b = 1.3, l = 1), "cm"),
          plot.title = element_text(size = plot_title_size)
    )

    print(htmltools::tagList(
        div(style = "display: inline-block; width: 49%;", 
            ggplotly(pipe_task_staging_plot, tooltip = "text") %>% 
              layout(hoverlabel = list(align = "left")) %>% 
              highlight(on = "plotly_click", off = "plotly_doubleclick", opacityDim = 0.05) %>% 
              set_ggplotly_font()) %>% toWebGL(),
        div(style = "display: inline-block; width: 49%;", 
            ggplotly(pipe_task_realtime_plot, tooltip = "text") %>% 
              layout(hoverlabel = list(align = "left")) %>% 
              highlight(on = "plotly_click", off = "plotly_doubleclick", opacityDim = 0.05) %>% 
              set_ggplotly_font()) %>% toWebGL()
        )
      )

  
  ####
  #### More than 2 groups to compare or multiple pipeline runs for the same pipeline
  ####
  }else {

    shared_data_tasks_plot <- SharedData$new(pipe_task_data_plot, key = ~name, group = pipe)

    ## If a pipeline was run more than once, we modify how we plot the points
    if(n_runs_max > 1){
      task_points_layer <- geom_point(aes(color = group), 
                                      size = point_size, 
                                      alpha = point_alpha)
    }else{
      task_points_layer <- geom_point(aes(color = group), 
               size = point_size,
               alpha = point_alpha)
    }
    
    runtime_vs_realtime_plot <- ggplot(shared_data_tasks_plot,
                                       aes(x = realtime_mins,
                                           y = staging_time_mins, 
                                           text = paste("Task name: ",name_short,"\n",
                                                        "run_id :",run_id,"\n",
                                                        "Submission time: ",waittime,"\n",
                                                        "Staging time: ",staging_time,"\n",
                                                        "Execution time: ",real_time,
                                                        sep=""))
                                       ) +
    task_points_layer +
    labs(
      x = "Task real time (minutes)",
      y = "Task staging time (minutes)",
      title = "Task staging and real times",
      color = "group"
    ) +
      seqera_light_theme() + 
      scale_color_manual(values = groups_color_palette)  +
      theme(plot.title = element_text(size = plot_title_size))
    
    print(htmltools::tagList(
    ggplotly(runtime_vs_realtime_plot, tooltip = "text") %>% 
      layout(hoverlabel = list(align = "left")) %>% highlight(on = "plotly_click", off = "plotly_doubleclick") %>%
      set_ggplotly_font() %>% toWebGL()
    )
  )
    
  } ## End of if-else for multi-group

  ## Select only columns we will use in the table
  pipe_task_data_table <- pipe_task_data_plot %>%
    select(group,run_id,name_short,hash,
           waittime,real_time,staging_time,
           cpus,memory,pcpu,pmem,rss,volCtxt,invCtxt,readBytes,writeBytes,
           executor,cloudZone,machineType,name,status)
  
  if(grepl("cost",profile)){
  ## Add accurate cost from cost_data_pipe_task_table
    accurate_task_cost <- cost_data_pipe_task_table %>%
      select(group,run_id,hash,cost) %>%
      mutate(hash = paste0(substr(hash, 1, 2), "/", substr(hash, 3, nchar(hash))))
    
    pipe_task_data_table <- full_join(pipe_task_data_table,accurate_task_cost,
                                      by = c("group","run_id","hash"))
  }
  
  ## Tasks table
  shared_data_tasks_table <- SharedData$new(pipe_task_data_table, key = ~name, group = pipe)
  font.size <- "12"
  rgba_colors <- sapply(groups_color_palette, hex_to_rgba, alpha = row_alpha_value)[1:length(unique(pipe_task_data_table$group))]
  
  # Define base column names that are common to both scenarios
  base_col_names <- c(
    "Group" = "group",
    "Run ID" = "run_id", 
    "Task<br/>hash" = "hash", 
    "Task name short" = "name_short",
    "Executor" = "executor",
    "Cloud<br/>zone" = "cloudZone",
    "Instance type" = "machineType",
    "Wait<br/>time" = "waittime",
    "Staging<br/>time" = "staging_time",
    "Real<br/>time" = "real_time",
    "Requested<br/>CPUs" = "cpus",
    "Requested memory<br/>(GiB)" = "memory",
    "Observed CPU<br/>(%)" = "pcpu",
    "Observed memory<br/>(%)" = "pmem",
    "Peak RSS<br/>(GiB)" = "rss",
    "Read<br/>bytes" = "readBytes",
    "Write<br/>bytes" = "writeBytes",
    "VolCtxt" = "volCtxt",
    "InvCtxt" = "invCtxt",
    "Task name" = "name",
    "Status" = "status"
  )
  
  # Add cost column if it exists
  col_names <- if("cost" %in% colnames(pipe_task_data_table)) {
    c(base_col_names[1:10], "Cost" = "cost", base_col_names[11:21])
  } else {
    base_col_names
  }
  
  # We need to select the actual column names from the data frame, not the display names
  pipe_task_data_table_filtered <- pipe_task_data_table %>%
    select(all_of(unname(col_names)))
  
  # Create a new SharedData object with the filtered data
  shared_data_tasks_table_filtered <- SharedData$new(pipe_task_data_table_filtered, key = ~name, group = pipe)
  
  # Create the datatable
  pipe_task_table <- div(
    class = "scrollable-table",
    datatable(
      shared_data_tasks_table_filtered,
      class = 'display',
      extensions = c('Buttons'),
      escape = FALSE,
      colnames = col_names,
      selection = "none",
      rownames = FALSE,
      options = list(
        autoWidth = FALSE,
        language = list(search = 'Filter:'),
        pageLength = 10,
        order = list(list(2, 'asc')),
        dom = 'Bfrtip',
        buttons = list(
          list(
            extend = 'csv',
            text = 'Download task table as CSV',
            filename = 'task_table'
          )
        ),
        initComplete = JS(
          "function(settings, json) {",
          "$('table').css({'font-size': '17px'});",
          "}"
        )
      )
    ) %>%
    formatStyle(
      'Group',
      target = 'row',
      backgroundColor = styleEqual(
        names(rgba_colors),
        rgba_colors
      )
    )
  )
  
  print(htmltools::tagList(
    tags$style(HTML("
  .dataTable thead th {
    background-color: #160f26 !important;
    color: white !important;
    text-align: left !important;
    white-space: nowrap;
  }
  .dataTable tbody td {
    text-align: left !important;
    white-space: nowrap;
  }
  .scrollable-table {
    width: 100%;
    overflow-x: auto;
  }
  /* Style for the download button */
  .dt-button {
    background-color: #160F26 !important;
    border: none !important;
    color: white !important;
    padding: 10px 10px !important;
    text-align: center !important;
    text-decoration: none !important;
    display: inline-block !important;
    font-size: 17px !important;
    margin: 4px 2px !important;
    cursor: pointer !important;
    border-radius: 5px !important;
  }
  .dt-button:hover {
    background-color: #0DC09D !important;
  }
")
    ),
  pipe_task_table))
  
  cat("\n\n")
  cat(sprintf('<div style="margin-bottom: 40px;"></div>'))
}
```
